SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-05 scipy-1.0/paper.tex
capitalized Airspeed Velocity

The airspeed velocity (\texttt{asv}\cite{asvref}) library enables benchmarking Python packages
over their lifetimes, and the performance of the SciPy code base was monitored
with \texttt{asv} starting in February of 2015 (PR \#4501). In addition to ensuring that
unit tests are passing, confirming 
that performance generally
remains constant or improves over the commit hash history of the project allows
us to objectively measure that our code base is improving, to empower
scientific applications.

>>>>

The Airspeed Velocity (\texttt{asv}\cite{asvref}) library enables benchmarking Python packages
over their lifetimes, and the performance of the SciPy code base was monitored
with \texttt{asv} starting in February of 2015 (PR \#4501). In addition to ensuring that
unit tests are passing, confirming 
that performance generally
remains constant or improves over the commit hash history of the project allows
us to objectively measure that our code base is improving, to empower
scientific applications.
